A Fredholm operator approach to the plate buckling problem

### 2018-08-16 doc/draft-01/08append2.tex
Updating appendix

Suppose that $\Omega$ is a bounded simply connected domain and that
$E = \R^{2} \setminus \Omega$ is its exterior.
Let $\Gamma = \partial \Omega$ denote the boundary of $E$.
For a given function $\bh$ on the boundary, 
the exterior velocity boundary value problem is given by:
\begin{align}
\Delta \bu + \omega^{2} \bu &= \nabla p \quad \bx \in E \, ,\\
\nabla \cdot \bu &= 0 \quad \bx \in E \, ,\\
\bu &= \bh \quad \bx \in \Gamma \, . \\
\end{align}
Let $\sigma$ denote the stress tensor associated with the velocity
field $\bu$, i.e.
\begin{equation}
\sigma = -p I + e(\bu) \, ,
\end{equation}
where $e(\bu)$ is the strain tensor given by
\begin{equation}
e(\bu) = D\bu + D\bu^{T} \, .
\end{equation}
Let $\bn$ denote the outward normal to the boundary $\Gamma$, then
the surface traction $\ff$ on the boundary $\Gamma$ is given 
by
\begin{equation}
\ff = \sigma \cdot \bn
\end{equation}
Analogous to the Helmholtz equation, we need to impose radiation conditions
at $\infty$.
We propose the following radiation conditions for the Stokes-Helmholtz 
equation
\begin{equation}
\lim_{r\to \infty} \sqrt{r} \left| \ff - i \omega \bu \right| \to 0 \, ,
\label{eq:radcond}
\end{equation}
uniformly in direction.

@@

\begin{proof}
Since $\bu$ satisfies the radiation condition, we have that
\begin{equation}
\lim_{r\to\infty} \int_{|\by|=r} | \ff - i \omega \bu|^2 ds = 
\lim_{r\to\infty} \int_{|\by| =r} \left( |\ff|^2 + |\omega|^2|\bu|^2 + 2 \text{Im} 
\left( \omega \bu\cdot \ff \right) ds \label{eq:raddecayproof1}
\right) = 0 \, . 
\end{equation}
Since $\bu$ satisfies the Stokes-Helmholtz equation $E \cap B_{r}(0)$,
using a couple of applications of the divergence theorem, we have that
\begin{equation}
\int_{E\cap B_{r}(0)} |e(\bu)|^2 dV = -\int_{\Gamma} \bu \cdot \overline{\ff} ds
+ \int_{|\by|=r} \bu \cdot \overline{\ff} ds + \overline{\omega}^2 
\int_{E \cap B_{r}(0)} |\bu|^2 dV \,. \label{eq:raddecayproof2}
\end{equation}
Combining~\cref{eq:raddecayproof1,eq:raddecayproof2}, we get
\begin{equation}
\lim_{r\to\infty} \int_{|\by|=r}\left(|\ff|^2 + |\omega|^2 |\bu|^2 \right) ds 
+ 2\text{Im}(k)\int_{E \cap B_{r}(0)} \left(|e(\bu)|^2 + |\omega|^2 |\bu|^2 
\right) dV = -2\text{Im} \int_{\Gamma} \omega \bu \cdot \overline{\ff} dS \, .
\end{equation}
\end{proof}

@@

\begin{thm}
(Uniqueness Dirichlet)
Suppose that $\text{Im}(\omega)>0$ and 
that $\bu$ is a radiating solution to the Stokes-Helmholtz
equation in $E$ with $\bu =0$ on the boundary $\Gamma$, then
$u \equiv 0$ in $E$.
\end{thm}

>>>>

Suppose that $\Omega$ is a bounded simply connected domain and that
$E = \R^{2} \setminus \Omega$ is its exterior.
Let $\Gamma = \partial \Omega$ denote the boundary of $E$.
For a given function $\bh$ on the boundary, 
the exterior velocity boundary value problem is given by:
\begin{align}
\Delta \bu + \omega^{2} \bu &= \nabla p \quad \bx \in E \, ,\\
\nabla \cdot \bu &= 0 \quad \bx \in E \, ,\\
\bu &= \bh \quad \bx \in \Gamma \, . \\
\end{align}
Let $\sigma$ denote the stress tensor associated with the velocity
field $\bu$, i.e.
\begin{equation}
\sigma = -p I + e(\bu) \, ,
\end{equation}
where $e(\bu)$ is the strain tensor given by
\begin{equation}
e(\bu) = \frac{1}{2}\left(D\bu + D\bu^{T} \right) \, .
\end{equation}
Let $\bn$ denote the outward normal to the boundary $\Gamma$, then
the surface traction $\ff$ on the boundary $\Gamma$ is given 
by
\begin{equation}
\ff = \sigma \cdot \bn
\end{equation}
Analogous to the Helmholtz equation, we need to impose radiation conditions
at $\infty$.
We propose the following radiation conditions for the Stokes-Helmholtz 
equation
\begin{equation}
\lim_{r\to \infty} \sqrt{r} \left| \ff - i \omega \bu \right| \to 0 \, ,
\label{eq:radcond}
\end{equation}
uniformly in direction.

@@

\begin{proof}
Since $\bu$ satisfies the radiation condition, we have that
\begin{equation}
\lim_{r\to\infty} \int_{|\by|=r} | \ff - i \omega \bu|^2 ds = 
\lim_{r\to\infty} \int_{|\by| =r} \left( |\ff|^2 + |\omega|^2|\bu|^2 + 2 \text{Im} 
\left( \omega \bu\cdot \ff \right) ds \label{eq:raddecayproof1}
\right) = 0 \, . 
\end{equation}
Since $\bu$ satisfies the Stokes-Helmholtz equation $E \cap B_{r}(0)$,
using a couple of applications of the divergence theorem, we have that
\begin{align}
\int_{E\cap B_{r}(0)} |e(\bu)|^2 dV &= \int_{E\cap B_{r}(0)} \left< e(\bu), \overline{e(\bu)} \right> dV  \\
&= \frac{1}{2}\left(\int_{E\cap B_{r}(0)} \left< e(\bu),\overline{D\bu} \right> + \left< e(\bu),\overline{D\bu}^{T} \right> \right) dV \\
&= \int_{E\cap B_{r}(0)} \left< e(\bu),\overline{D\bu} \right> dV \\
&= \int_{\partial }
-\int_{\Gamma} \bu \cdot \overline{\ff} ds
+ \int_{|\by|=r} \bu \cdot \overline{\ff} ds + \overline{\omega}^2 
\int_{E \cap B_{r}(0)} |\bu|^2 dV \,. \label{eq:raddecayproof2}
\end{equation}
Combining~\cref{eq:raddecayproof1,eq:raddecayproof2}, we get
\begin{equation}
\lim_{r\to\infty} \int_{|\by|=r}\left(|\ff|^2 + |\omega|^2 |\bu|^2 \right) ds 
+ 2\text{Im}(k)\int_{E \cap B_{r}(0)} \left(|e(\bu)|^2 + |\omega|^2 |\bu|^2 
\right) dV = -2\text{Im} \int_{\Gamma} \omega \bu \cdot \overline{\ff} dS \, .
\end{equation}
\end{proof}

@@

\begin{thm}
(Uniqueness Dirichlet)
Suppose that $\text{Im}(\omega)\geq 0$ and 
that $\bu$ is a radiating solution to the Stokes-Helmholtz
equation in $E$ with $\bu =0$ on the boundary $\Gamma$, then
$u \equiv 0$ in $E$.
\end{thm}
